% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt
\usepackage[papersize={8.5in,11in}]{geometry}
\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
\setmainfont{Minion Pro} % Main document font
\usepackage{xltxtra}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Shih-Kai Lin}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{}

\begin{center}
{\large\bf Shih-Kai Lin} 
\end{center}
\medskip\hrule height 1pt
\begin{center}
{2121 El Paseo St Apt 1307 \\   Houston, TX 77054 \\ (832) 907-9035 \\ shihkailin78@gmail.com} 
\end{center} \vfill % forces letterhead to top of page
 
 
\opening{Dear Sir/Madam:} 
 
\noindent %PARAGRAPH ONE: State reason for letter, name the position or type 
%of work you are applying for and identify source from  which  you 
%learned   of   the  opening.  (i.e.  Career  Development  Center, 
%newspaper, employment service, personal contact). 
It is my pleasure to learn of the opening for the Data Scientist position through LinkedIn. With solid experience and a strong passion for data analysis, I believe I am prepared to make immediate contribution to your company.
 
\noindent %PARAGRAPH  TWO:  Indicate why you are interested in the position, 
%the company, its products, services - above all, stress what  you 
%can  do  for  the employer. If you are a recent graduate, explain 
%how your academic background makes you a qualified candidate  for 
%the  position.  If  you have practical work experience, point out 
%specific achievements or unique qualifications. Try not to repeat 
%the  same  information  the reader will find in the resume. Refer 
%the reader to the enclosed resume or application which summarizes 
%your  qualifications,  training,  and experiences. The purpose of 
%this section is to strengthen your resume  by  providing  details 
%which bring your experiences to life. 
The following are highlights of my qualifications for the Data Scientist position:
\begin{itemize}
	\item 8 years of experience in large quantity statistical data analysis.
	\item Hands-on experience in image and signal processing.
	\item Expertise in statistics software ROOT equivalent to R.
  \item Hands-on experience in relational database from design to implementation with MySQL.
	\item Extensive experience in algorithm design and problem solving in C++ in Linux.
	%\item Working knowledge in parallel programming with OpenMP.
\end{itemize}

With my interdisciplinary training in physics and computer science, I have been efficiently utilizing my computer skills to analyze a large amount of scientific data and making statistical inferences such as parameter estimation and linear regression. The fundamental training in science also makes me a quick learner of mathematical theories, programming languages, program libraries and software packages. I believe my strengths and experience will provide you with an invaluable resource.

\noindent %PARAGRAPH THREE: Request a personal interview and  indicate  your 
%flexibility as to the time and place. Repeat your phone number in 
%the letter and offer assistance to help in a speedy response. For 
%example,  state that you will be in the city where the company is 
%located on a certain date and would like to set up an  interview. 
%Or,  state  that  you  will  call  on a certain date to set up an 
%interview. End the letter by thanking  the  employer  for  taking 
%time to consider your credentials. 
I would welcome a personal interview to tell you more about my qualifications, as well as what I can do for your company. I appreciate your taking the time to review my credentials and experience. Again, thank you for your consideration. 
 
\closing{Sincerely yours,} 
 

 
\encl{resume}					% Enclosures

\end{letter}
 

\end{document}
