% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt
\usepackage[papersize={8.5in,11in}]{geometry}
\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
\usepackage{xltxtra}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Shih-Kai Lin}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{HR Recruiter for Software Developer Position \\
Mireaux Management Solutions \\
12802 Willow Centre Dr. \\
Houston, TX 77066}

\begin{center}
{\large\bf Shih-Kai Lin} 
\end{center}
\medskip\hrule height 1pt
\begin{center}
{2121 El Paseo St Apt 1307 \\   Houston, TX 77054 \\ (864) 349-5588 \\ shihkailin78@gmail.com} 
\end{center} \vfill % forces letterhead to top of page
 
 
\opening{Dear recruiter:} 
 
\noindent %PARAGRAPH ONE: State reason for letter, name the position or type 
%of work you are applying for and identify source from  which  you 
%learned   of   the  opening.  (i.e.  Career  Development  Center, 
%newspaper, employment service, personal contact). 
As I learned of the software developer position through the University of Houston's JOBank database, I felt eager to pursue it to offer my skills and enthusiasm in client oriented software development.
 
\noindent %PARAGRAPH  TWO:  Indicate why you are interested in the position, 
%the company, its products, services - above all, stress what  you 
%can  do  for  the employer. If you are a recent graduate, explain 
%how your academic background makes you a qualified candidate  for 
%the  position.  If  you have practical work experience, point out 
%specific achievements or unique qualifications. Try not to repeat 
%the  same  information  the reader will find in the resume. Refer 
%the reader to the enclosed resume or application which summarizes 
%your  qualifications,  training,  and experiences. The purpose of 
%this section is to strengthen your resume  by  providing  details 
%which bring your experiences to life. 
Back in the day when I was fulfilling my mandatory military service, I served in the computer information department due to my Bachelor's degree in computer science. That was a time when our unit started to migrate the management of equipment parts from papers to computers. I, together with several comrades, took over a windows application written in Borland Delphi in its early stage and started to develop and enrich the functionality of the application. The familiarity of MS Visual C++ 4 from my undergraduate education helped me pick up any GUI programming in no time. My communication skills made me understand the needs of the users and the motivation of learning new technologies such as ODBC helped realize any functions the users requested. With the advances of technology, recently I developed a web-based 3D detector event display with MySQL, JavaScript, jQuery, AJAX, PHP and WebGL trying to serve as many people in the collaboration as possible. This again demonstrates my self-motivation of embracing new technologies and my interest in developing client oriented software.
 
\noindent %PARAGRAPH THREE: Request a personal interview and  indicate  your 
%flexibility as to the time and place. Repeat your phone number in 
%the letter and offer assistance to help in a speedy response. For 
%example,  state that you will be in the city where the company is 
%located on a certain date and would like to set up an  interview. 
%Or,  state  that  you  will  call  on a certain date to set up an 
%interview. End the letter by thanking  the  employer  for  taking 
%time to consider your credentials. 
I would welcome a personal interview to tell you more about my qualifications, as well as what I can do for Mireaux Management Solutions. My phone number is (864) 349-5588 and I am available anytime for an interview. I appreciate your taking the time to review my credentials and experience. Again, thank you for your consideration. 
 
\closing{Sincerely yours,} 
 

 
\encl{resume}					% Enclosures

\end{letter}
 

\end{document}
