\documentclass[11pt,letterpaper]{moderncv}
\usepackage{libertine}    %% or newtxtext for times 
\moderncvstyle{classic}
\moderncvcolor{green}
\usepackage[scale=0.75]{geometry}

\name{Shih-Kai}{Lin}
\title{Research Assistant}
\address{2121 El Paseo St Apt 1307}{Houston, TX, 77054}
\phone[mobile]{+1~(832)~907~9035}
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{shihkailin78@gmail.com}
%\homepage{www.johndoe.com}
\social[linkedin]{shihkailin}
%\social[twitter]{jdoe}
%\social[github]{jdoe}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}
\quote{}


\begin{document}
\makecvtitle


\section{Objective}
Looking for a full-time job title utilizing multidisciplinary experience in programming, algorithm design and statistical analysis to solve real world problems.


\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{Aug 2014}{Doctor of Philosophy in Physics}{University of Houston}{Houston, TX}{\textit{GPA: 3.867/4.0}}{}
\cventry{2003--2005}{Master of Science in Physics}{National Taiwan University}{Taipei, Taiwan}{}{}
\cventry{1996--2001}{Bachelor of Science in Computer Science}{National Taiwan University}{Taipei, Taiwan}{}{}


%\section{Summary of Qualifications}
%\begin{itemize}
%	\item Hands-on experience in HTML, python and relational database from design to implementation with MySQL.
%	\item 8 years of experience in large quantity statistical data analysis.
%	\item 8 years of experience in algorithm design and problem solving in C++ in Linux.
%	\item 3 years of experience in concurrent job management with Sun Grid Engine on National Energy Research Scientific Computing Center.
%\end{itemize}

\section{Experience}

\cventry{2009--present}{Research Assistant}{University of Houston}{Houston, TX}{}{
\begin{itemize}%
	\item	Analyze data for neutron production by cosmic ray muons.
  \item Developed a reconstruction algorithm to reconstruct the incident position and the track of cosmic ray muons.
  \item Monte Carlo simulation on photoelectron production by photons and electron transport in Bakelite.
  \item Developed a web based 3D muon event display with WebGL and MySQL technology.
	\item Designed and built a small resistive plate chamber for monitoring the gas composition.
  \item Experience in operating radioactive sources such as $^{137}$Cs, $^{90}$Sr and $^{60}$Co for resistive plate chamber response study.
  \item Designed and built a collimator for shielding and collimating $^{60}$Co.
  \item During hardware installation, led a team of technicians to route 400 electronic cables from a 10m deep pool to the electronics control room in a week.
\end{itemize}}
\cventry{2005--2008}{Research Assistant}{Academia Sinica}{Taipei, Taiwan}{}{
\begin{itemize}%
	\item Analyzed data used for dark matter exclusion plots.
  \item Developed an algorithm utilizing Fast Fourier Transform spectra to reject near-threshold detector noise.
  \item Utilizing pulse shape discrimination(PSD) technique to lower detector threshold.
	\item Calibrated the Ge detector with $^{137}$Cs, $^{60}$Co, $^{55}$Fe, $^{32}$P, etc.
	\item Maintained the Ge detector located 28m away from the core of No.1 reactor of Kuo-Sheng Nuclear Power Station.
\end{itemize}}
\cventry{2003--2005}{Research Assistant}{National Taiwan University}{Taipei, Taiwan}{}{
\begin{itemize}%
  \item Measured and published a paper on the transport properties of Indium Gallium Nitride.
  \item Extensive experience in high vacuum and low temperature experiments.
\end{itemize}}
\cventry{2001--2003}{Lieutenant}{Mandatory Military Service}{}{}{
\begin{itemize}
	\item Maintained and developed a windows application for database management of parts of radio equipment with Borland Delphi.
\end{itemize}
}


\section{Honors and Professional Memberships}
\cvitem{Mar 2013}{American Physical Society}
\cvitem{Nov 2009}{Golden Key International Honour Society}
\cvitem{2005}{Government Fellowship for Studying Abroad from Ministry of Education, Taiwan}


\section{Conference Talks}
\cvitem{Apr 2013}{Shih-Kai Lin, ``A Geometric Method for Measuring Muon Induced Neutrons at Daya Bay", APS April Meeting 2013}


\section{Languages}
\cvitem{Chinese}{Native}
\cvitem{English}{Fluent}


\section{Computer Skills}

\cvitem{Language}{\textsc{C/C++}, \textsc{MS Visual C++ 4.0}, \textsc{Borland Delphi}, \textsc{HTML}, \textsc{Python}, \textsc{Bash}, SQL, \textsc{JavaScript}, PHP, AJAX, \LaTeX}

\cvitem{Software}{\textsc{MySQL}, \textsc{SQLite}, \textsc{phpMyAdmin}, \textsc{Apache}, \textsc{Squid}, \textsc{Origin}, MATLAB}
\cvitem{System}{\textsc{Windows}, \textsc{Linux} (both \textsc{Debian} and \textsc{Red Hat} based)}


\end{document}